---
title: "A General Organization Template for R Programs"
output: html_notebook
---


```{r setup, results='hide'}
your_folder <- c("C:","Users","Documents","MyFolder")
knitr::opts_knit$set(root.dir = normalizePath(paste(your_folder,sep="\\"))) 
```




<h2>Abstract</h2>
"IN USING THIS TEMPLATE, THE TEXT YOU ARE REPLACING IS ALWAYS INDICATED SURROUNDED BY QUOTATION MARKS AND WRITTEN IN ALL CAPS. YOU
WILL REPLACE EVERY INSTANCE OF THESE WITH YOUR OWN WORK. WHAT YOU ARE TO REPLACE EACH INSTANCE WITH IS INDICATED AT THE END OF
EACH INSTANCE PRECEDING THE ELLIPSES AND WITHIN VERTICAL BARS. IF NO ADDITIONAL EXPLANATION IS REQUIRED, THEN EACH INSTANCE THAT 
YOU WILL REPLACE WILL SIMPLY INDICATE WHAT IT IS THAT YOU ARE TO REPLACE IT WITH. BE SURE TO CHANGE YOUR WORKING DIRECTORY FOR 
YOUR CODE BY EDITING THE CHUNK PRECEDING THIS TO THE FOLDER YOU ARE WORKING WITHIN; NO FURTHER DIRECTORY CHANGES WITHIN CHUNKS 
WILL BE NEEDED. FINALLY, BE SURE TO CHANGE THE TITLE AT THE BEGINNING OF THIS DOCUMENT.  |INSERT BASIC EXPLANATION OF YOU CODE 
HERE...|"




<h2>Procedure</h2>
"YOU WANT TO DIVIDE YOUR ENTIRE CODE DOCUMENT INTO SNIPPETS OF CODE THAT ARE RELATED IN SOME MANNER IN ORDER TO PRESENT YOUR
FINDINGS IN AN EASILY DIGESTIBLE MANNER TO YOUR AUDIENCE. FOR THIS TEMPLATE, WE WILL USE THREE CHUNKS. IF YOUR PROCEDURE REQUIRES
MORE CHUNKS, THEN SIMPLY ADDEND CHUNKS BELOW THE THIRD CHUNK. IF YOUR PROCEDURE REQUIRES LESS CHUNKS, THEN SIMPLY REMOVE ALL
UNECESSARY CHUNKS.  |ADD COMMENTARY AND YOUR THOUGHT PROCESS BEHIND YOUR CODE HERE...|"



<h3>"(OPTIONAL)SUB-DIVISION 1"</h3>
"IF YOUR PROCEDURE NEEDS TO BE SUB-DIVIDED INTO INDIVIDUAL SECTIONS, THEN PROCEED THROUGH THIS TEMPLATE. IF YOUR PROCEDURE IS 
SUCCINT ENOUGH TO NOT NEED TO BE SUB-DIVIDED, THEN SIMPLY REMOVE THE THIRD-LEVEL HEADINGS AND USE THE TEMPLATES BELOW THEM UNDER 
THIS CURRENT HEADER.  |INSERT SUB-DIVISION 1 EXPLANATION HERE...|"


```{r "chunk1.1"}
your_code_goes_here <- TRUE
```

"|INSERT CHUNK1.1 COMMENTARY HERE...|"


```{r "chunk1.2"}
your_code_goes_here <- TRUE
```

"|INSERT CHUNK1.2 COMMENTARY HERE...|"


```{r "chunk1.3"}
your_code_goes_here <- TRUE
```

"|INSERT CHUNK1.3 COMMENTARY HERE...|"



<h3>"(OPTIONAL)SUB-DIVISION 2"</h3>
"|INSERT SUB-DIVISION 2 EXPLANATION HERE...|"


```{r "chunk2.1"}
your_code_goes_here <- TRUE
```

"|INSERT CHUNK2.1 COMMENTARY HERE...|"


```{r "chunk2.2"}
your_code_goes_here <- TRUE
```

"|INSERT CHUNK2.2 COMMENTARY HERE...|"


```{r "chunk2.3"}
your_code_goes_here <- TRUE
```

"|INSERT CHUNK2.3 COMMENTARY HERE...|"



<h3>"(OPTIONAL)SUB-DIVISION 3"</h3>
"|INSERT SUB-DIVISION 3 EXPLANATION HERE...|"


```{r "chunk3.1"}
your_code_goes_here <- TRUE
```

"|INSERT CHUNK3.1 COMMENTARY HERE...|"


```{r "chunk3.2"}
your_code_goes_here <- TRUE
```

"|INSERT CHUNK3.2 COMMENTARY HERE...|"


```{r "chunk3.3"}
your_code_goes_here <- TRUE
```

"|INSERT CHUNK3.3 COMMENTARY HERE...|"




<h2>Conclusions</h2>
"|INSERT CONCLUDING THOUGHTS OR REFLECTIONS ON YOUR PROJECTS HERE...|"




<h2>(Optional)Works Cited</h2>
"THIS IS AN OPTIONAL SECTION. IF YOU MAKE REFERENCES TO OTHER WORKS, STUDIES, WEBSITES, ETC, THEN LIST THESE AS CITATIONS USING
THE BULLETS BELOW. FOR THIS TEMPLETE, WE WILL USE THREE REFERENCE WORKS. IF YOUR PROJECT REFERENCES MORE WORKS, THEN SIMPLY ADDED
BULLETS BELOW THE THIRD BULLET AS NECESSARY. IF YOUR PROJECT REFERNECES LESS WORKS, THEN SIMPLY REMOVE ALL UNNECESSARY BULLETS. IF
YOUR CODE IS YOUR OWN SELF-CONTAINED WORK, THEN DELETE THIS ENTIRE SECTION. FOR THIS TEMPLATE, NO EXPLANATIONS ARE NEEDED TO BE 
INSERTED BETWEEN THE ABOVE SECOND-LEVEL HEADER AND THE BULLETS BELOW:  |DELETE THIS TEXT IF USING THIS WORKS CITED SECTION...|"

* "REFERENCE1"

* "REFERENCE2"

* "REFERENCE3"

