---
title: "R-INLA Blow Flies Analysis Tutorial"
output: html_notebook
---

```{r setup, results='hide'}
knitr::opts_knit$set(root.dir = normalizePath(paste("D:","`Grad_Research","Rudy_RA_Work","R_Tutorial_Blow_Flies",sep="\\"))) 
```

## Overview

The purpose of this tutorial is to provide instructions for the implementation of a few basic procedures available through the
R-INLA package. In order to make use of these procedures, we will need to also make use of several other R packages.

There are two primary operations that we will be employing in this tutorial:
   
  * Creating an adjacency matrix for the three study areas in the provided data set
  * Performing a Bayesian hierarchical Poisson model, specifically a BYM model



## Initialization

We will divide our preliminary procedures into two groups: directory setup and package loading.


### Directory Setup

We begin our tutorial by taking care of a few minor housekeeping procedures. First, we make sure that our entire R workspace is
clear of variables using the rm() function (which is identical to the remove() function). And second, we set our working directory
for R. What this is is essentially making sure that the program knows that the area it is performing calculations in is the folder
where your data is.

```{r a}
remove(list=ls())
setwd(paste("D:","`Grad_Research","Rudy_RA_Work","R_Tutorial_Blow_Flies",sep="\\"))
```

Note that the above directory is accurate only for my own computer. For yourself, what you will want to do is replace all of the
above strings with strings representing each folder level you have saved your data into. For example, if the location of your file
is C:\\Users\\Me\\MyDocuments\\Geography\\This_Class, you will want the above setwd() to read: 
setwd(paste("C:","Users","Me","MyDocuments","Geography","This_Class",sep="\\\\")).

### Package Loading

With the directory business out of the way, we move on to loading all of the packages that we will be making use of in this tutorial.
What the require() function does is load a package into R so that you can use it in your code. Note that if you currently DO NOT
have the listed package installed, the package load will fail. If this happens to you, then all you need to do is go to the "Tools"
menu at the top of RStudio and click the first option, "Install Packages": just write in the desired package, and after a brief
period of loading, run the require function on the package again.

```{r b}
require(INLA)
inla.setOption(scale.model.default=FALSE)
require(splancs)
require(sp)
require(fields)
require(maptools)
require(lattice)
require(abind)
require(spdep)
require(fastmatch)
```


## From Shapefile to Adjacency Matrix
>"Using inla.graph: produces the graph from a shape file with information on all the area boundaries and uses a combination of 
functions from different R packages." -Rudy Banerjee

As Rudy explains in the quote above, what we're now going to do is use a bunch of combinations of the loaded packages' functions
to convert the provided shapefile into an adjacency matrix, which will output to your "Plots" tab in Rstudio. To do this, we first
will convert the shapefile to a special type of R dataframe, then will use that special dataframe object to generate a list of
neighbors, and next will output an INLA .GRAPH into the folder. We will then define a variable to hold the location string for the
outputted graph for use later. Finally, we will use the INLA package to read the graph and record it as a variable object, and then
we will the image() function to output our adjacency matrix to our "Plots" tab for the world to see.

```{r c}
z.gen <- readShapePoly("shp/all 3 overlay.shp")
temp <- poly2nb(z.gen)
nb2INLA("z.graph", temp)
z.adj <- paste(getwd(),"/z.graph",sep="")

H <- inla.read.graph(filename="z.graph")
image(inla.graph2matrix(H),xlab="",ylab="")
```

Just as in the previous section, we will need to consider our filepath locations in order for our functions to, well, function. So
long as you extract your shp.zip file to the same hypothetical folder C:\\Users\\Me\\MyDocuments\\Geography\\This_Class above, then
you should be able to run the above code in your session without any trouble.



## The BYM Model

We now move on to the second primary operation in this tutorial: creating the BYM model. Our procedure will be as follows: we start
by defining the formula we will use for our BYM model; next will read and record our provided .csv file (that is, our data being 
modeled) onto a variable; will then define the outcome variable, compute the expected outcome for this variable, and verify that both
values have a common mean; and finally use the INLA package to perform our BYM model. We will finish our tutorial by outputting a
summary of our model, using the convenient summary() function. Here we go.

```{r d}
formula <- y ~ 1 + f(ID, model="bym",graph=z.adj)

library(readr)
Voronois <- read_csv("D:/`Grad_Research/Rudy_RA_Work/R_Tutorial_Blow_Flies/shp/Overlay.csv")

y <- Voronois$TotalPhormia
E <- Voronois$Area * sum(y)/sum(Voronois$Area)

if (isTRUE(abs(mean(y)-mean(E))<1e-10)){
  print("mean(y) and mean(E) are the same")
}

mod.Z <- inla(formula,family="poisson",
                         data=Voronois,E=E,
                         control.compute=list(dic=TRUE))
summary(mod.Z)
```

In the above chunk, the variable 'y' is the outcome variable, and the variable 'E' is the expected outcome of this variable. The
if statement simply outputs confirmation as to whether or not your mean(y) and mean(E) are the same value (well, 
technically-speaking, not that they are the same, but that their difference is a neglible artifact of rounding errors). Lastly, as
always, be aware that the read_csv() function is reading a folder location, specifically *my* folder location, meaning that you
will once again have to replace the above character string with the one specific to where you have your files saved on your
computer.
